### 2023-02-26 manuscript.tex
Adjusting author contributions, statements of conflict of interest, and funding [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/dd2c5af597f1c7b6482aa346aca45b009ab10d25.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/dd2c5af597f1c7b6482aa346aca45b009ab10d25/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4276630098

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/afbbe55b2ad8febebb104fc9358170f15b3a4596/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/afbbe55b2ad8febebb104fc9358170f15b3a4596}{SORTEE-Github-Hackathon/manuscript@afbbe55}
on February 26, 2023.

@@

\begin{itemize}
\tightlist
\item
  Conceptualization: RCO, BPME, KH, EJH, LLSR, PHPB
\item
  Investigation: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
\item
  Methodology: RCO, BPME, KH, EJH, LLSR, PHPB
\item
  Project administration: RCO
\item
  Software: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
\item
  Visualization: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
\item
  Writing -- original draft: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
\item
  Writing -- review and editing: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
\item
  Resources: PHPB
\end{itemize}

@@

RCO was funded by the U.S. Department of Energy, Office of Science, Office of Biological and Environmental Research, Earth and Environmental Sciences Division, Data Management program under contract number DE-AC02-05CH11231.

@@

\hypertarget{ethics-declarations---competing-interests}{%
\subsection{Ethics declarations - Competing interests}\label{ethics-declarations---competing-interests}}

RCO was recently offered a position to work at GitHub (on July 15, 2022) and will start employment at GitHub on August 23, 2022.
Initial discussion of publishing this manuscript began in July 2021 and all work on the manuscript took place while RCO was an employee at Lawrence Berkeley National Laboratory.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/dd2c5af597f1c7b6482aa346aca45b009ab10d25/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/dd2c5af597f1c7b6482aa346aca45b009ab10d25}{SORTEE-Github-Hackathon/manuscript@dd2c5af}
on February 26, 2023.

@@

\begin{itemize}
\tightlist
\item
  Conceptualization: RCO, BPME, KH, EJH, LLSR, PHPB
\item
  Investigation: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
\item
  Methodology: RCO, BPME, KH, EJH, LLSR, PHPB
\item
  Project Administration: RCO, PHPB
\item
  Software: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
\item
  Visualization: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
\item
  Writing - Original Draft: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
\item
  Writing - Review and Editing: RCO, BPME, KH, EJH, LLSR, ERS, MJG, VF, ADB, CBB, KMG, SSHS, AG, FH, HW, DGEG, PHPB
\item
  Resources: PHPB
\item
  Revisions: PHPB, ERS, RCO, KH, EH, FH
\end{itemize}

@@

RCO was funded by the U.S. Department of Energy, Office of Science, Office of Biological and Environmental Research, Earth and Environmental Sciences Division, Data Management program under contract number DE-AC02-05CH11231.
PHPB was supported by the Science without Borders program and the Brazilian National Council for Research and Technological Development (CNPq-SwB-GDE 142493/2013-0).

@@

\hypertarget{conflict-of-interest-statement}{%
\subsection{Conflict of Interest Statement}\label{conflict-of-interest-statement}}

On July 15, 2022, RCO was offered a position to work at GitHub and became an employee on August 23, 2022.
Initial discussion of publishing this manuscript began in July 2021 and all work on the manuscript prior to the first revision was done while RCO was an employee at Lawrence Berkeley National Laboratory.
The authors declare that there is no conflict of interest that could be perceived as prejudicing the impartiality of the research reported.
